Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-04-07 reviews/response.Rmd

response

# Reviewer 2 comments {-}

> What is the definition of "period"? Is the period defined on the grouping or on the granularity?Is the period denoted by P or (R, P) in Definition 6? From Pages 6 Line 55 to Page 7 Line 7, period was referred to an integer (7), and two time granularities (one year and 400 years). Are they consistent?

Period is defined for a pair of granularities $(G, H)$. In Definition 6, the period is defined by $P$, which is briefly defined while explaining Definition 6. Thanks for pointing out the inconsistencies. We have now made it consistent.

> What is the definition of "grouping"? Though "G groups into H" was defined in Definition 5, there is not a notation of grouping $(G, H)$ until we see grouping $(day, month)$ at
Page 7 Line 7. Please rephrase the sentence each month is a grouping of the same number of days over years on Page 7 Line 5.

We have used the term "pair" instead "grouping" to avoid conflict with the definition of "groups into" and rephrased the sentence.

> What is the definition of aperiodic linear granularities? On Page 11, Definition 10, $M_i$ are aperiodic linear granularities. If $M_i$ are aperiodic, then is $M$ also an aperiodic linear granularity? What is the relationship between aperiodic linear granularity and aperiodic
cyclic granularity?

### 2021-04-07 main.Rmd
Reviewer 2 + other minor issues - addressed

In general, any circular granularity relating two linear granularities can be expressed as
$$
  C_{(G, H)}(z) = \lfloor z/P(B,G) \rfloor\mod P(G,H),
$$
where $H$ is periodic with respect to $G$ with regular mapping and period $P(G,H)$. Table&nbsp;\ref{tab:definitions} shows several circular granularities constructed using minutes as the bottom granularity.

@@

  * $C_{\ell,m'}(z)$ is circular and $C_{m',m}(z)$ is quasi-circular
\begin{equation} \label{eq:multifromsingle-quasi1}
C_{G_\ell,G_{m}}(z) = C_{G_{\ell},G_{m'}}(z) + P(\ell, m')C_{G_{m'},G_{m}}(z)
\end{equation}

  * $C_{\ell,m'}(z)$ is quasi-circular and $C_{m',m}(z)$ is circular
\begin{equation} \label{eq:multifromsingle-quasi2}
C_{G_\ell,G_{m}}(z)  = C_{G_{\ell},G_{m'}}(z) + \sum_{w=0}^{C_{m',m}(z) -1}(\vert T_{w} \vert)
\end{equation}
where, $T_w$ is such that $G_{m'}(w) = \bigcup_{z \in T_w}G_{\ell}$ and $\vert T_w \vert$ is the cardinality of set $T_w$.

@@

(ref:bothcust) Energy consumption of a single customer shown with different distribution displays, and granularity arrangements. Two granularities are used: 1. hour of the day; and 2. weekday/weekend. Plot a shows granularity 1 faceted by granularity 2; plots b and c shows the reverse mapping. Plot a allows comparison of usage by workday within each hour of the day using side-by-side boxplots, showing that on work days there is more consumption early in the day. Plots b and c examine the temporal trend of consumption over the course of a day, separately for the type of day. Plot b uses an area quantile to emphasize the time component; e.g., median consumption shows prolonged high usage in the morning on weekdays. Plot c uses a violin plot emphasize subtler distributional differences across hours, showing that morning use on weekdays is bimodal, and on some work days there is low usage possibly indicating the person is working from home or having a late start.

>>>>

In general, any circular granularity relating two linear granularities can be expressed as
$$
  C_{G, H}(z) = \lfloor z/P(B,G) \rfloor\mod P(G,H),
$$
where $H$ is periodic with respect to $G$ with regular mapping and period $P(G,H)$. Table&nbsp;\ref{tab:definitions} shows several circular granularities constructed using minutes as the bottom granularity.

@@

  * $C_{G_{\ell},G_{m'}}(z)$ is circular and $C_{G_{m'},G_{m}}(z)$ is quasi-circular
\begin{equation} \label{eq:multifromsingle-quasi1}
C_{G_\ell,G_{m}}(z) = C_{G_{\ell},G_{m'}}(z) + P(\ell, m')C_{G_{m'},G_{m}}(z)
\end{equation}

  * $C_{G_{\ell},G_{m'}}(z)$ is quasi-circular and $C_{G_{m'},G_{m}}(z)$ is circular
\begin{equation} \label{eq:multifromsingle-quasi2}
C_{G_\ell,G_{m}}(z)  = C_{G_{\ell},G_{m'}}(z) + \sum_{w=0}^{C_{G_{m'},G_{m}}(z) -1}(\vert T_{w} \vert)
\end{equation}
where, $T_w$ is such that $G_{m'}(w) = \bigcup_{z \in T_w}G_{\ell}$ and $\vert T_w \vert$ is the cardinality of set $T_w$.

@@

(ref:bothcust) Energy consumption of a single customer shown with different distribution displays, and granularity arrangements. Two granularities are used: 1. hour of the day; and 2. weekday/weekend. Plot a shows granularity 2 faceted by granularity 1; plots b and c shows the reverse mapping. Plot a allows comparison of usage by workday within each hour of the day using side-by-side boxplots, showing that on work days there is more consumption early in the day. Plots b and c examine the temporal trend of consumption over the course of a day, separately for the type of day. Plot b uses an area quantile to emphasize the time component; e.g., median consumption shows prolonged high usage in the morning on weekdays. Plot c uses a violin plot emphasize subtler distributional differences across hours, showing that morning use on weekdays is bimodal, and on some work days there is low usage possibly indicating the person is working from home or having a late start.
